Theoretical prediction of disrupted Min oscillation in flattened \emph{Escherichia coli}

### 2015-06-20 paper/plos.tex
first two jeff-assigned responses

%% biology~\cite{lawson2013spatial, robb2014stochastic,
%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
In this paper we use Huang's original 2003
model~\cite{huang2003dynamic}, which has been widely
used~\cite{hattne2005stochastic,huang2004min,kerr2006division, fange2006noise} in both
deterministic and stochastic variants, to study flattened cells of
$0.4\micron$ thickness that are similar to those observed by M\"annik
\emph{et al.}~\cite{mannik2009bacterial}.

@@

The predictions of the stochastic model are roughly similar to the
experimental results in terms of irregularity of the locations of
maxima, although there are locations on the edges of the cells where
experiment shows maxima occurring that we never see in our simulations,
suggesting that the model does not precisely reflect the experiment.
We also note that the stadium shapes in Fig.~\ref{randst-plot-ave}
appear to have maxima location irregularity that is qualitatively
similar to our irregular shapes and to experiment.

>>>>

%% biology~\cite{lawson2013spatial, robb2014stochastic,
%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
In this paper we use Huang's original 2003
model~\cite{huang2003dynamic}, which has been widely
used~\cite{hattne2005stochastic,huang2004min,kerr2006division,
  fange2006noise} in both deterministic and stochastic variants, to
study flattened cells of $0.4\micron$ thickness that are similar to
those observed by M\"annik \emph{et al.}~\cite{mannik2009bacterial}.
\fixme{This allows us to test the performance of this important model
  in more extreme situations than has been done previously, furthering
  considerably our understanding of how and to what extent it breaks
  down. It will be valuable in the future to compare these results
  against similar tests of more recent models, in order to better
  understand how they gain advantage.}

@@

The predictions of the stochastic model are roughly similar to the
experimental results in terms of irregularity of the locations of
maxima, although there are locations on the edges of the cells where
experiment shows maxima occurring that we never see in our
simulations, suggesting that the model does not precisely reflect the
experiment.  We also note that the stadium shapes in
Fig.~\ref{randst-plot-ave} appear to have maxima location irregularity
\fixme{within a small number of periods} that is
qualitatively similar to our irregular shapes and to experiment.
